---
title: "Have federal agencies become more partisan over time?"
author:
- name: Samiha Bhushan
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: my@email.com
shorttitle: Do members of Congress have an increasing level of influence on the outcome
  of federal agency financial rulemaking?
output:
  html_document:
    df_print: paged
    code_folding: hide
    toc: true
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  O
keywords: keywords
wordcount: X
bibliography: r-references.bib
floatsintext: no
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: University of Wisconsin-Madison
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
# Sets defaults for R chunks
knitr::opts_chunk$set(echo = TRUE)
requires <- c("tidyverse", # tidyverse includes dplyr and ggplot2
              "broom",
              "haven", 
              "devtools",
              "magrittr",
              "margins",
              "lmtest",
              "viridisLite",
              "truncnorm",
              "ggridges",
              "here",
              "fuzzyjoin",
              "editData",
              "readxl")
## Install any you don't have
to_install <- c(!requires %in% rownames(installed.packages()))
install.packages(c(requires[to_install], "NA"), repos = "https://cloud.r-project.org/" )
## Load all required R packages
library(tidyverse)
library(broom)
library(haven)
library(magrittr)
library(margins)
library(here)
library(readxl)
library(ggplot2); theme_set(theme_bw()) # global plot theme
## Colorblind and greyscale print-friendly scales
library(viridisLite)
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(..., begin = 0, end = .7)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(..., begin = 0, end = .7)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



#Research Questions

Does variation in financial agencies' independence affect congressional success in rulemaking?

How does variation in the number of congressional coalitions affect congressional success in financial agency rulemaking?

Does either conformity or deviation from the party of the President affect congressional success?

Do members of Congress increasingly utilize partisan rhetoric over time to influence success within financial agency rulemaking?
 - Does variation in partisan rhetoric affect congressional success?

#Abstract 
(125 words)
The outcomes to federal rulemaking proposals in response to congressional lobbying is integral towards understanding how government institutions work. However, federal agencies vary in level of independence, as measured by how responsive they are to public demands. Previous studies have shown that federal agency rulemaking, especially within the financial divisions, has become more independent over time, with agencies becoming less responsive to public comments. Using data from prior studies conducted by Dr. Jennifer Selin and Dr. Devin Judge-Lord, I seek to study whether this pattern can be seen within the congressional sphere — i.e. if financial federal agencies are responsive to congressmembers’ demands. I also attempt to see if there may be any change of influence for those within the same or opposing party of the President.


# Methods
I will gather data from 40 rules issued by financial agencies, including but not limited
to the Consumer Financial Protection Bureau, the Treasury Department, and the Office of
the Comptroller of the Currency. I focus on public comments issued by members of
Congress and focus on whether their demands were ultimately fulfilled in the final rule.
The research design additionally combines data from a previous study conducted by
Jennifer L. Selin, who determined an estimate of the level of structural independence for
several agencies during the Obama administration. My study will also include rules during
the subsequent Trump administration, wherein the Senate majority switched to the
Republican party. I will compare and contrast rules from both eras to determine if
influence from political parties have grown over time, including determining if there is an
increased presence of politicians commenting on policies.
I will also use textual analysis in addition to the hand coding to see if elected officials
use more partisan rhetoric over time. In this study, “partisan rhetoric” refers to an
individual making positive assertions about their own party or negative assertions about
the opposing party. I will also examine whether the demands of elected officials that are
the same party as the President are increasingly met over those of the opposing party.

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results



### Simulated Data

Does either conformity or deviation from the party of the President affect congressional success?



One measure of agency independence may be examined by studying the effects of congressmember's party affiliation and whether it conforms with the President's party affiliation.

We have the following data for 10 congressmembers:

`Success`: whether agencies fullfilled Congressmembers' demands, measured between -2 and 2.

`Party`: "1" for if the party is the same for the congressmember and the President and "0" if the party is different between the congressmember and the President.

`Independence`: The estimates of agency independence, derived from Selin's data.

`Coalitions` : sizes of coalitions that the congressmember is affiliated with.


Table \@ref(tab:data-sim) shows ten rows of simulated data.

```{r data-sim}
library(tidyverse)
library(tibble)
library(msm)
library(kableExtra)
congressional_success <- sample(x = c(-2, -1, 0, 1, 2), 1000, prob = c(0.1, 0.3, .1, 0.4, 0.1), replace = T)
d = tibble(rule_id = c(1:1000, rep(1001:1500, 2)),
           congress_id = sample(1:2000),
           coalitions  = c(rep(1, 1000), rep(2, 1000)),
           congressional_success = c(congressional_success, sort(congressional_success)), 
           coalition_size = rtnorm(1000, mean = 5, sd= 10, lower = 1) %>% rep(2) %>% round(), 
           party_affiliation = sample(x = c(0,1), 2000, replace = T, prob = c(0.7, .3)),
           independence = sample(x = c(4.1,1.643,0.174,0.218,2.269), 2000, replace = T),
           comments= c(rtnorm(1000, mean = 10000, sd = 100000, lower = 100), rep(1, 1000)) %>%
sample() %>% round() , 
           cong_support = c(rtnorm(1000, mean = 1, sd = 5, lower = 0), rep(0, 1000)) %>% sample() %>% round() )             
d %>% sample_n(10) %>% dplyr::select(rule_id, congress_id, everything())
```

# Hypotheses

H1: Members of Congress of the same party as the President have their demands fullfilled more often than congressmembers that are of a different politcal party. That is, the relationship between congressional success and agency independence differs by party affiliation. 

H0: There is no difference in congressional success for members of Congress of the same of differing party of the President. That is, the relationship between congressional and agency independence does not differ by party affiliation. 

# Linear regression

The dependent variable is congressional success. For congressmember $i$, let congressional success be $y_i$ in the model $y_i = \beta_0 + ... + \epsilon_i$. $\beta_0$ is the predicted salary, $\hat{y}$, when all other variables in the model are 0.


---

## A model

Does the model, $y_i = \beta_0 + \beta_1*party_i + \epsilon_i$, test the relationship of interest? 
```{r congress_model, fig.height = 1}
model <- lm(congressional_success ~ party_affiliation, data = d) 
m <- model %>% 
  tidy(conf.int = TRUE) 
m
ggplot(m %>% filter(term != "(Intercept)")) + 
  aes(x = term,
      y = estimate, 
      ymin = conf.low, 
      ymax = conf.high) + 
  geom_pointrange() + 
  geom_hline(yintercept = 0, color = "grey") + 
  coord_flip() + 
  labs(x="", y="OLS Estimate")
```

```{r summary}
# scatterplots
ggplot(d) + 
  aes(x = party_affiliation, y = congressional_success) + 
  geom_point(aes(alpha = coalition_size)) 
p <- ggplot(d) + 
  aes(x = party_affiliation, y = congressional_success) + 
  geom_point(aes(alpha = coalition_size))
p
```

### data plot
```{r congress_plot}
# illustrating with yhat formula; more easily done with augment()
b0 <- m$estimate[1]
b1 <- m$estimate[2]
p +
  geom_line(aes(color = "Deviation", # yhat for opposition party
                y = b0 + b1*1) ) + 
  geom_line(aes(color = "Conformity", # yhat for same party
                y = b0 + b1*0) )  +
  geom_ribbon(aes(ymax = b0 + b1*1, 
                  ymin = b0 + b1*0), alpha = .1, color = NA)
```

t-test (compare model output to simple t-test of difference in mean `congressional success` by `party`).
```{r}
# tidy model output object
m 
# t-test
t.test(congressional_success ~ party_affiliation, data = d) %>% tidy()
```

```{r hist-coalitions-sim, fig.width=2, fig.height=2,  out.width = "30%"}
ggplot(d, aes(x = congressional_success)) + geom_histogram()+ labs(x = "Congressional Success")
ggplot(d, aes(x = independence)) + geom_histogram()+ labs(x = "Independence")
ggplot(d, aes(x = coalition_size)) + geom_histogram()+ labs(x = "Coalition size")
```


### Multiple linear regression
$y_i = \beta_0 + \beta_1*party_i + \beta_2*independence_i + \epsilon_i$
```{r}
model_1 <- lm(congressional_success ~ independence + party_affiliation, data = d)
      augment()
summary(model_1)
m1 <- model_1 %>% 
  tidy(conf.int = TRUE) 
m1
ggplot(m1 %>% filter(term != "(Intercept)")) + 
  aes(x = term,
      y = estimate, 
      ymin = conf.low, 
      ymax = conf.high) + 
  geom_pointrange() + 
  geom_hline(yintercept = 0, color = "grey") + 
  coord_flip() + 
  labs(x="", y="OLS Estimate")
```

### Let's plot the results against our data!
```{r congress_party_plot}
# illustrating with yhat formula; more easily done with augment()
b0 <- m1$estimate[1]
b1 <- m1$estimate[2]
b2 <- m1$estimate[3]
p +
  geom_line(aes(color = "Deviation", # yhat for opposition party
                y = b0 + b1*1 + b2*party_affiliation) ) + 
  geom_line(aes(color = "Conformity", # yhat for same party
                y = b0 + b1*0 + b2*party_affiliation) )  +
  geom_ribbon(aes(ymax = b0 + b1*1+ b2*party_affiliation, 
                  ymin = b0 + b1*0+ b2*party_affiliation), alpha = .1, color = NA)
```

### Fit 
Let's also plot the residuals. Aside from interpretation, we want to know where our model is a better or worse fit with the data, especially if residuals seem to vary systematically over the range of our data.

`augment` computes tidy residuals, among other cool things.
```{r congress_residuals}
m1 <- augment(model_1)
p + 
  geom_line(aes(y = m1$.fitted)) + # with .fitted from augment()
  geom_point(aes(y = m1$.fitted), shape = 1, alpha = .2) + # with .fitted from augment()
  geom_segment(aes(xend = independence, yend = m1$.fitted ), alpha = .2, size = 2)
ggplot(m1) +
  aes(y = .resid, x = party_affiliation) + 
  geom_point(aes(color = party_affiliation)) + 
  scale_color_viridis_c() + 
  ## to show how risiduals are the distance between an 
  ## observation and the regression line:
  geom_hline(yintercept = 0, color = "dark grey") +
  geom_text(x= mean(m1$independence), y = 0, 
            label = "Regression line") +
  geom_col(aes(fill = party_affiliation), alpha = .2, position ="identity") +
  ## + labels:
  labs(title = "Residuals (Observed - Predicted Independence)",
       y = "Residuals") 
```

### AIC and BIC


```{r}
glance(model_1)
```

### Simulated Results

Unsurprisingly this model yields no significant results (Figure \@ref(fig:model-success-plot-sim), Table \@ref(tab:mediation-sim)). With lobbying success as the dependent variable, the coefficient on the main variable of interest would be interpreted as a $\beta_{logmasscomments}$ increase in the five-point influence scale of lobbying success for each one-unit increase in the logged number of comments.


```{r new_data}
library(googlesheets4)
comments <- read_sheet("https://docs.google.com/spreadsheets/d/1HBjG32qWVdf9YxfGPEJhNmSw65Z9XzPhHdDbLnc3mYc/edit?usp=sharing")
load("/Users/samihabhushan/Documents/financial-rulemaking/data/members.Rdata")
agency_data <- read_excel("/Users/samihabhushan/Documents/financial-rulemaking/data/federal_agencies_estimate.xlsx")
```


```{r president_scores}
members %<>% 
  mutate(nominate_pres = case_when(
  congress < 111 ~ 0.693,
  congress >111 & congress <115 ~ -0.358,
  congress > 115 & congress <117 ~ 0.403,
  congress > 117 ~ -0.320))

members %<>% mutate(
nominate_diff = nominate.dim1-nominate_pres)

comments %<>% full_join(members, by = "icpsr", copy = FALSE)
comments %<>% mutate(Agency = str_remove(id.x, "-.*") )
comments %<>% full_join(agency_data, by = "Agency", copy = FALSE)
```
## Real data model

```{r new_summary}
# scatterplots
ggplot(comments) + 
  aes(x = nominate_diff, y = success) + 
  geom_point(aes(alpha = congress.x)) 
# add color by Gender, and save plot as p for future use
p <- ggplot(comments) + 
  aes(x = nominate_diff, y = success, color = party_name) + 
  geom_point(aes(alpha = congress.x)) + scale_color_discrete()
p

```

```{r real congress_ols_estimate}
model <- lm(success ~ nominate_diff, data = comments) 
m <- model %>% 
  tidy(conf.int = TRUE) 
m
ggplot(m %>% filter(term != "(Intercept)")) + 
  aes(x = term,
      y = estimate, 
      ymin = conf.low, 
      ymax = conf.high) + 
  geom_pointrange() + 
  geom_hline(yintercept = 0, color = "grey") + 
  coord_flip() + 
  labs(x="", y="OLS Estimate")
m$.fitted
```

```{r real congress_plot}
# illustrating with yhat formula; more easily done with augment()
b0 <- m$estimate[1]
b1 <- m$estimate[2]
p +
  geom_line(aes(
                y = b0 + b1*1) ) + 
  geom_line(aes(
                y = b0 + b1*0) )  +
  geom_ribbon(aes(ymax = b0 + b1*1, 
                  ymin = b0 + b1*0), alpha = .1, color = NA)
```

```{r hist-coalitions, fig.width=2, fig.height=2,  out.width = "30%"}
ggplot(comments, aes(x = success)) + geom_histogram()+ labs(x = "Congressional Success")
ggplot(comments, aes(x = Estimate)) + geom_histogram()+ labs(x = "Independence")
ggplot(comments, aes(x = nominate_diff)) + geom_histogram()+ labs(x = "Diff in nominate scores")
```
### Multiple linear regression
$y_i = \beta_0 + \beta_1*nominate_i + \beta_2*independence_i + \epsilon_i$
```{r}
model_1 <- lm(success ~ nominate_diff + Estimate, data = comments)
      augment()
summary(model_1)
m1 <- model_1 %>% 
  tidy(conf.int = TRUE) 
m1
ggplot(m1 %>% filter(term != "(Intercept)")) + 
  aes(x = term,
      y = estimate, 
      ymin = conf.low, 
      ymax = conf.high) + 
  geom_pointrange() + 
  geom_hline(yintercept = 0, color = "grey") + 
  coord_flip() + 
  labs(x="", y="OLS Estimate")

```


### AIC and BIC


```{r, eval= FALSE}

model_2 <- lm(congressional_success ~ nominate_diff, data = comments)

m2 <- augment(model_2)


ggplot(d) + 
  aes(x =  nominate_diff, y = congressional_success) + 
  geom_point() + scale_color_discrete() +
  geom_line(aes(y = m2$.fitted)) + # with .fitted from augment()
  geom_point(aes(y = m2$.fitted), shape = 1, alpha = .2) + # with .fitted from augment()
    geom_segment(aes(xend = nominate_diff, yend = m2$.fitted ), alpha = .2, size = 2)


```

# Discussion

Wendy E. Wagner describes a salient issue within the rulemaking process, wherein well-funded interest groups attempt to overwhelm the decision making process in a regulatory context. She states "information capture refers to the excessive use of information and related information costs as a means of gaining control over regulatory decision-making in informal rulemakings." In her study, she describes excessive use of telephone calls, emails, memorandas, and petitions of appeal to bombard overstretched agency staff, and therefore forces them to disregard their own expert opinions on the rule, as well as an inability to properly process other sides of the issue. As congresspeople are often considered to be a part of well-funded interest groups, especially taking into consideration that many congresspeople jointly write letters to petition for or against an issue. As such, this may skew the overall success of the Congressmembers' demands. Even if congressmembers do not employ information capture to influence the success of their demands, they may be associated with the interest groups that do. It is important to create this distinction as the results are dependant on how rulemaking agencies consider congressmembers' asks and their own levels of federal independence, rather than the tactics used by an interest group.

A federal agencies levels of independence does not end up being the biggest influence on whether a demand is fulfilled, rather its a failure for interest groups to self-process information they give agencies, i.e. filter failure. Even agencies with a high level of independence and have a commited to openness and transperency will not be able to avoid the issue of information capture. Regulatory solutions to a diverse amount of interest groups is no longer possible, given that much of the information is buried within mountains of information. Wagner continues, "once excessive information begins to gum up the works, simple fixes are no longer possible. Radical institutional overhaul becomes the only viable remedy." The idea of information theory underscores the idea of ensuring communications to large governing bodies such as regulatory agencies is efficient and effective encapsulates the issue for all interested parties on a given rule. 

The financial rulemaking process is often opaque and difficult to understand, which exacerbates the issue. Well-funded groups, paired with congressional pressure, imploy extremely technical language as well overly detailed arguments for unrelated aspects of the rule, therefore gumming up the rulemaking process. Wagner claims "To preserve issues for litigation, affected parties are thus best-advised to provide comments that are specific, detailed, and well documented. This seemingly reasonable requirement for specificity again encourages interested parties to provide too much documentation, too many specifics, and too much detail, rather than too little." Given there are increasing information costs for overly technical comments, this becomes the basis of well-funded interest groups' comment issuing process. Further, increasing amounts of direct partipation with the federal agencies may cause the federal agencies to increasingly rely on the experts within the interest groups, rather than retaining their own experts and objective opinions.  

Wagner provides several means of avoiding the information capture process, including an increase the civic participation of the agency staff, as effective agency leadership and an awareness of the information capture process is powerful towards maintaining objectivity. However, she postulates that it is not enough, as agency staff "will face an uphill legal battle to surmount all of the one-sided pressures." Moreover, hiring of agency staff must be trasparent and enable only those without a strong favoring for a certain interest group, which is a difficult and nebulous statement. Wagner also suggests providing the public with "a number of legislative and executive innovations, such as cost-benefit analysis" in order to allow the information to be more digestible for a layperson as well as an opportunity to focus on different implications of the rule. 

Interestingly, Wagner also provides a mechnaism that allows congressmembers' to alleviate, rather than contribute, to the issue. While civic-minded agency staff is poweful, civic-minded beaurocrats within Congress and the White House is more powerful. Drafting regulations to limit the level of information distributed may be effective in preventing the information capture process. However, it is then imperative for congressmembers' to maintain objectivity within the rulemkaing process, as it stands this is not the case as congressmembers' often issue public comments with their own opinions on the matter. This would require a complete overhaul of the rulemaking process as it stands, as well as additional judicial reviews and oversight boards to maintain politicians' objectivity. 


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
